---
title: "R Notebook"
output: rmarkdown::github_document
---

```{r}
#Importing SQLite library
library("RSQLite")
```

```{r}
# Connecting to the Pitchfork database
sqlite <- dbDriver("SQLite")
pitchforkdb <- dbConnect(sqlite, "database.sqlite")
```

```{r}
# Listing all the tables in the Pitchfork database
dbListTables(pitchforkdb)
```

```{r}
# Viewing the artists table
artists <- dbSendQuery(pitchforkdb, "SELECT * FROM artists LIMIT 10")
dbFetch(artists)
```

```{r}
# Viewing the content table
content <- dbSendQuery(pitchforkdb, "SELECT * FROM content LIMIT 5")
dbFetch(content)
```

The content table is qualitative with the actual reviews embedded, so we won't use that one for exploration. 

```{r}
# Viewing the genres table
genres <- dbSendQuery(pitchforkdb, "SELECT * FROM genres LIMIT 10")
dbFetch(genres)
```

```{r}
# Viewing the labels table
labels <- dbSendQuery(pitchforkdb, "SELECT * FROM labels LIMIT 10")
dbFetch(labels)
```

```{r}
# Viewing the reviews table
reviews <- dbSendQuery(pitchforkdb, "SELECT * FROM reviews LIMIT 10")
dbFetch(reviews)
```

```{r}
# Viewing the years table
years <- dbSendQuery(pitchforkdb, "SELECT * FROM years LIMIT 10")
dbFetch(years)
```

We will join tables "labels", "genre", and "year" onto the "reviews: table. The "content" table is unnecessary, and information from the "artists" table is already included in the "reviews" table.

```{r}
# Joining the table
joined <- dbSendQuery(pitchforkdb, "SELECT *
                                    FROM reviews r
                                    LEFT JOIN labels l
                                    ON r.reviewid = l.reviewid
                                    LEFT JOIN genres g
                                    ON r.reviewid = g.reviewid
                                    LEFT JOIN years y
                                    ON r.reviewid = y.reviewid")
df <- dbFetch(joined)
df
```

Let's get names of all columns, so that we can drop some of them. 

```{r}
#Column names preview
colnames(df)
```

We will delete the ones that we don't need.

```{r}
# Deleting columns
df$url <- NULL
df$author <- NULL
df$pub_weekday <- NULL
df$reviewid..14 <- NULL
df$reviewid..16 <- NULL
df$reviewid..18 <- NULL
```

The final dataframe looks like:

```{r}
# Checking the final dataframe
head(df)
```

At this point, I'd like to save the dataframe as csv. 

```{r}
write.csv(df, file = "pitchfork_scores.csv")
```

